### 2025-11-11 submissions/03-jpam-RR/manuscript_main.tex
bootstrapped results!

Since log odds coefficients from multinomial logit models are difficult to interpret directly, I compute the predicted probabilities of each identity choice at different anti-Asian bias levels, holding other covariates constant. This approach provides more intuitive insights into how bias influences the likelihood of selecting each identity category and is easier to understand.

>>>>

Since log odds coefficients from multinomial logit models are difficult to interpret directly, I compute the predicted probabilities of each identity choice at different anti-Asian bias levels, holding other covariates constant and summarizing results with the median across 1{,}000 bootstrap resamples (with percentile-based 95\% confidence intervals). This approach provides more intuitive insights into how bias influences the likelihood of selecting each identity category and is easier to understand.

### 2025-11-11 submissions/03-jpam-RR/manuscript_tab_fig.tex
bootstrapped results!

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_all.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_all.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_all.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_all.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans. First-generation Asian Americans are foreign-born individuals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent. Third-generation Asian Americans are native-born individuals with native-born parents and at least one Asian-born grandparent.}}
\end{figure}
\end{center}

@@

% % Marginal Effects: All Generations (after main Multinomial Logit Model plot)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
% \label{fig:marginal-effects-all}
% \includegraphics[width=0.9\linewidth]{optimized_marginal_effects_all.png}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
% \end{figure}
% \end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_second_aw.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_second_aw.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_second_wa.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_second_wa.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_second_wa.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_second_wa.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

% \begin{subfigure}{.48\textwidth}
% \caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_second_aw.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_second_wa.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
% \end{figure}
% \end{center}

@@

% Top row: Anti-Asian Bias and Female
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_value_simple.png}\label{subfig:pp-secgen-aw-bias}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_value_simple.png}\label{subfig:pp-secgen-wa-bias}
\end{subfigure}

@@

% Second row: Female
\begin{subfigure}{.48\textwidth}
\caption{Female (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_Female_simple.png}\label{subfig:pp-secgen-aw-female}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_Female_simple.png}\label{subfig:pp-secgen-wa-female}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of anti-Asian bias or gender, holding other covariates at their means.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_one.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_one.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_two.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_two.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_two.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_two.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_three.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_three.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_three.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_three.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
% \label{fig:marginal-effects-third-grandparental}
% \begin{subfigure}{.45\textwidth}
% \caption{One Asian Grandparent}\label{subfig:oneasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_one.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.45\textwidth}
% \caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_two.png}
% \end{subfigure}

@@

% \begin{subfigure}{.45\textwidth}
% \caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_three.png}
% \end{subfigure}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals.}}
% \end{figure}
% \end{center}

>>>>

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_all_generations_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_all_generations_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_all_generations_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_all_generations_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans. First-generation Asian Americans are foreign-born individuals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent. Third-generation Asian Americans are native-born individuals with native-born parents and at least one Asian-born grandparent. Each curve reports the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals use the percentile method from the same draws.}}
\end{figure}
\end{center}

@@

% % Marginal Effects: All Generations (after main Multinomial Logit Model plot)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
% \label{fig:marginal-effects-all}
% \includegraphics[width=0.9\linewidth]{boot_me_all_generations.png}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point reports the median marginal effect across 1{,}000 bootstrap resamples, and 95\% confidence intervals come from the associated bootstrap percentile bounds. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
% \end{figure}
% \end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals follow the corresponding bootstrap percentile limits.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with White fathers and Asian mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals follow the corresponding bootstrap percentile limits.}}
\end{figure}
\end{center}

@@

% \begin{subfigure}{.48\textwidth}
% \caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_second_AW.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_second_WA.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point corresponds to the median marginal effect across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
% \end{figure}
% \end{center}

@@

% Top row: Anti-Asian Bias and Female
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_value.png}\label{subfig:pp-secgen-aw-bias}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_value.png}\label{subfig:pp-secgen-wa-bias}
\end{subfigure}

@@

% Second row: Female
\begin{subfigure}{.48\textwidth}
\caption{Female (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_Female.png}\label{subfig:pp-secgen-aw-female}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_Female.png}\label{subfig:pp-secgen-wa-female}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of anti-Asian bias or gender, holding other covariates at their means. Curves plot the median predicted probability across 1{,}000 bootstrap resamples, with 95\% confidence intervals given by the bootstrap percentile bounds.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

@@

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_Female.png}
\end{subfigure}

@@

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
% \label{fig:marginal-effects-third-grandparental}
% \begin{subfigure}{.45\textwidth}
% \caption{One Asian Grandparent}\label{subfig:oneasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_oneAsian.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.45\textwidth}
% \caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_twoAsian.png}
% \end{subfigure}

@@

% \begin{subfigure}{.45\textwidth}
% \caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_threeAsian.png}
% \end{subfigure}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each estimate is the median across 1{,}000 bootstrap resamples, and 95\% percentile confidence intervals accompany every point.}}
% \end{figure}
% \end{center}
